---
title: "Median Household Incomes in Canada"
author: "Alexander Ondrus"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source("FSA_CMA_Intersects.R")
```

## The Problem

* Have a product/service targeted to households with a certain household income
  * How to know which markets have enough areas with a high (or low) enough median household income to be viable target markets?
  * Once you have chosen a market, how do you target your marketing to specific areas?

## The Solution

* Statistics Canada performs a Census every 4 years
* Profiles of each _Forward Sortation Area (FSA)_ (similar to a US Zip Code) include the median household income
* Need to identify Census Metropolitan Areas (cities and their surrounding communities) that have enough FSAs in the target range
* I've created a [web app](https://alexondrus.shinyapps.io/CanCensusMedIncome/) that displays this information and allows the user to download the results

## Example

Here's the visual that is generated when the user selects Vancouver from the list of Canadian Census Metropolitan Areas:

```{r van-eg, message=FALSE, warning=FALSE}
VancouverEg <- intersect_FSAs_join_data("Vancouver")
VancouverPlot <- FSA_CMA_plot(VancouverEg)
plot(VancouverPlot)
```

## Download

The 'Download' button allows the user to download the list of forward sortation areas along with the median household income for the chosen census metropolotian area.

Give it a try!